My title

### 2023-03-13 outputs/paper/paper.qmd
- Changed all variable/column names in cleaned dataset back to original - Applied these changes to all graphs and tables that used the former variable names - Deleted saving mean of variables as a csv in paper.qmd as it was giving an error

```{r}
# Summary statistics of our GSS data 
summ_gss <- cleaned_2016gss_data %>% 
  select(`Age.Group`, `Sex`, `Race`, `Personal.Income`, `Total.Family.Income`, 
         `Highest.Education.Obtained`, `Number.of.Children`, `Marital.Status`,
         `Level.of.Happiness`, `Weekly.Total.of.Internet.Use..Hours.`)
# sumtable(summ_gss,  title = "Summary Statistics of Our Variables", out = "kable")
## the final line doesn't work for some reason and i'm mad
```

@@

```{r}
#| label: fig-maritalandinternet
#| fig-cap: Weekly Total of Internet Use by Marital Status
#| echo: false
## Graph Marital Status VS. Internet Hours ##
mean_marital <- cleaned_2016gss_data %>%
  select(`Marital Status`,`Weekly Total of Internet Use (Hours)`) %>%
  group_by(`Marital Status`)%>%
  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
  pivot_wider(names_from = "Marital Status", values_from = c("Mean_total"))

@@

# save mean data
write_csv(mean_marital, "outputs/data/mean_marital.csv")

# use tidyverse-style code to pivot and summarise the data 
mean_marital |> ggplot(aes(x = variable, y = value)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Marital Status",
    y = "Internet Usage Hours"
  )
```

```{r}
#| label: fig-happyandinternet
#| fig-cap: Weekly Total of Internet Use by Level of Happiness
#| echo: false
## Graph Level of Happiness VS. Internet Hours##
mean_happy<- cleaned_2016gss_data %>%
  select(`Level of Happiness`,`Weekly Total of Internet Use (Hours)`) %>%
  group_by(`Level of Happiness`)%>%
  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
  pivot_wider(names_from = "Level of Happiness", values_from = c("Mean_total"))

@@

# save mean data
write_csv(mean_happy, "outputs/data/mean_happy.csv")

@@

```{r}
#| label: fig-educandinternet
#| fig-cap: Weekly Total of Internet Use by Highest Education Obtained
#| echo: false
## Highest Education Obtained VS. Internet Hours ##
mean_edu<- cleaned_2016gss_data %>%
  select(`Highest Education Obtained`,`Weekly Total of Internet Use (Hours)`) %>%
  group_by(`Highest Education Obtained`)%>%
  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
  pivot_wider(names_from = "Highest Education Obtained", values_from = c("Mean_total"))

@@

# save mean data
write_csv(mean_edu, "outputs/data/mean_edu.csv")

>>>>

```{r}
# Summary statistics of our GSS data 
summ_gss <- cleaned_2016gss_data %>% 
  select(age, sex, race, income, rincome, 
         degree, childs, marital,
         happy, wwwhr)
sumtable(cleaned_2016gss_data,  title = 'Summary Statistics of Our Variables', out = 'kable')
## the final line doesn't work for some reason and i'm mad
```

@@

```{r}
#| label: fig-maritalandinternet
#| fig-cap: Weekly Total of Internet Use by Marital Status
#| echo: false
## Graph Marital Status VS. Internet Hours ##
mean_marital<- cleaned_2016gss_data %>%
  select(marital,wwwhr) %>%
  group_by(marital)%>%
  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
  pivot_wider(names_from = "marital", values_from = c("Mean_total"))

@@

# use tidyverse-style code to pivot and summarise the data 
mean_marital |> ggplot(aes(x = variable, y = value)) + 
  geom_point() +
  theme(axis.text.x = element_text(angle = 45,hjust=1), 
        axis.line = element_line(colour = "black"),
        title = element_text(size = 12)) +
  labs(
    x = "Marital Status",
    y = "Internet Usage Hours"
  )
```
@fig-maritalandinternet displays the relationship between marital status and internet usage in 2016.

```{r}
#| label: fig-happyandinternet
#| fig-cap: Weekly Total of Internet Use by Level of Happiness
#| echo: false
## Graph Level of Happiness VS. Internet Hours##
mean_happy<- cleaned_2016gss_data %>%
  select(happy,wwwhr) %>%
  group_by(happy)%>%
  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
  pivot_wider(names_from = "happy", values_from = c("Mean_total"))

@@

@@

```{r}
#| label: fig-educandinternet
#| fig-cap: Weekly Total of Internet Use by Highest Education Obtained
#| echo: false
## Highest Education Obtained VS. Internet Hours ##
mean_edu<- cleaned_2016gss_data %>%
  select(degree, wwwhr) %>%
  group_by(degree)%>%
  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
  pivot_wider(names_from = "degree", values_from = c("Mean_total"))

@@
